A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-10-15 doc/large_strain.tex
split figures into 2, add subsections

\section{Matrix-free operator evaluation}
\label{sec:mf}
Classically in order to solve \eqref{eq:linear_system}, the matrix $\gz K$ and the force vector $\gz F$ corresponding to the discretization are assembled and
a direct or iterative solver is used to solve the linear system.
On modern computer architectures however, it turns out that loading data is significantly slower than performing the arithmetic operations when solving.
For this reason, recent implementations often focus on so-called matrix-free approaches. The idea is to perform the operations in the solver on-the-fly
rather than loading matrix elements from memory.
For iterative solvers, this is possible since it is sufficient to compute matrix-vector products.
%
The matrix-vector product $A x$ can be expressed by
\begin{align*}
 (Ax)_i &= \sum_j a(\gz N_i,\gz N_j) x_j \\
        &= \sum_K\sum_q \sum_j \tilde{a}(\gz N_i,\gz N_j)(\gz x_q) x_j w_q
\end{align*}
where in the last step $\tilde{a}_K(\varphi_i,\varphi_j)(\gz x_q)$ is a representation for the evaluation of the bilinear in one quadrature point and a quadrature rule is used.
For the sake of demonstration, let us assume $A$ represents a mass matrix. In this case, it holds
\begin{align*}
 \tilde{a}_K(N_i,N_j)(\gz x_q) = N_i(\gz x_q)N_j(\gz x_q).
\end{align*}
Further assuming that the number of the one-dimensional quadrature points $n$ matches the degree of the ansatz space plus one, the evaluation of all the shape functions ($n^d$)
in all quadrature points ($n^d$) has complexity $\mathcal{O}(n^{2d})$ in case we consider a problem in $d$ space dimensions. For the total matrix-vector product we get $\mathcal{O}(2n^{2d})$
and this is the same as for a regular matrix-vector where the entries are already precomputed. Assuming tensor product ansatz spaces and a tensor product quadrature rule, we can actually do better
than that. Indeed, the evaluation of all the shape functions in all the ansatz points can be rewritten as
\begin{lstlisting}
template<int k, int q>
void evaluate_dof_vector_in_all_quadrature_points
  (const double u[k][k][k],
   const double phi[k][q],
   double return_value[q][q][q])
{
  double tmp1[k][k][q] {};
  for (int i1=0; i1<k; ++i1)
    for (int i2=0; i2<k; ++i2)
      for (int q3=0; q3<q; ++q3)
        for (int i3=0; i3<k; ++i3)
          tmp1[i1][i2][q3] += u[i1][i2][i3]*phi[i3][q3];

@@

\begin{algorithm}[!ht]
  \SetKwInOut{Input}{Given}
  \SetKwInOut{Output}{Return}
  \Input{RHS FE vector $\gz x$, current FE solution $\gz u$,
  cacheed $c_1 := \mu - 2 \lambda \log(J)$ for each cell and quadrature point}
  \Output{action of the FE tangent \eqref{eq:algebraic_tangent} on $\gz x$}
  \ForEach{ element $K \in \Omega^h$ }{
        \ForEach{quadrature point $q$ on $K$}{
          evaluate $\gz \nabla_X \gz u^h$ \tcp*{2nd order}
          evaluate $\gz F = \gz I + \gz \nabla_X \gz u^h$ \tcp*{2nd order}
          evaluate $J = \rm{det}(\gz F)$ \tcp*{scalar}
          evaluate $\gz b = \gz F \cdot \gz F^T$ \tcp*{2nd order symmetric}
          evaluate $\gz g := \gz \nabla \gz x$ \tcp*{2nd order}
          evaluate $\gz \tau = \mu \gz b - c_1 \gz I$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{G}} \gz g = \gz g \cdot \gz \tau/J$ \tcp*{2nd order}
          ``submit'' contraction $\gz \nabla \gz N_i : \boldsymbol{\mathcal{G}} \gz g$\;
          evaluate $\gz g_s := \gz \nabla_{sym} \gz x$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{C}}\gz g_s = \left[2 c_1 \gz g_s + 2 \lambda\, \rm{tr}( \gz g_s) \gz I \right]/J$ \tcp*{2nd order symmetric}
          ``submit'' contraction $\gz \nabla_{sym} \gz N_i : \boldsymbol{\mathcal{C}}\gz g_s$ \;
        }
  }
  \caption{Matrix-free tangent cell operator: scalar cache}
  \label{alg:mf_scalar}
\end{algorithm}

@@

\begin{algorithm}[!ht]
  \SetKwInOut{Input}{Given}
  \SetKwInOut{Output}{Return}
  \Input{RHS FE vector $\gz x$,
  cached
  $c_1 := 2\left[\mu - 2 \lambda \log(J)\right]/J$,
  $c_2 := 2\lambda/J$ and $\gz \tau/J$ for each cell and quadrature point}
  \Output{action of the FE tangent \eqref{eq:algebraic_tangent} on $\gz x$}
  \ForEach{ element $K \in \Omega^h$ }{
        \ForEach{quadrature point $q$ on $K$}{
          evaluate $\gz g := \gz \nabla \gz x$ \tcp*{2nd order}
          evaluate $\boldsymbol{\mathcal{G}}\gz g = \gz g \cdot \left[\gz \tau/J \right]$ \tcp*{2nd order}
          ``submit'' contraction $\gz \nabla \gz N_i : \boldsymbol{\mathcal{G}} \gz g$ \;
          evaluate $\gz g_s := \gz \nabla_{sym} \gz x$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{C}} \gz g_s = c_1 \gz g_s + c_2 \, \rm{tr}(\gz g_s) \gz I$ \tcp*{2nd order symmetric}
          ``submit'' contraction $\gz \nabla_{sym} \gz N_i : \boldsymbol{\mathcal{C}} \gz g_s $ \;
        }
  }
  \caption{Matrix-free tangent cell operator, variant 1: cache second order Kirchhoff stress $\gz \tau$ and thereby avoid the need to evaluate refential quantities like $\gz F$ at runtime.}
  \label{alg:mf_tensor2}
\end{algorithm}

@@

\begin{algorithm}[!ht]
  \SetKwInOut{Input}{Given}
  \SetKwInOut{Output}{Return}
  \Input{RHS FE vector $\gz x$,
  cached $\gz \tau/J$ and $\boldsymbol{\mathcal{C}}$ for each cell and quadrature point}
  \Output{action of the FE tangent \eqref{eq:algebraic_tangent} on $\gz x$}
  \ForEach{ element $K \in \Omega^h$ }{
        \ForEach{quadrature point $q$ on $K$}{
          evaluate $\gz g := \gz \nabla \gz x$ \tcp*{2nd order}
          evaluate $\boldsymbol{\mathcal{G}} \gz g = \gz g \cdot \left[\gz \tau/J\right]$ \tcp*{2nd order}
          ``submit'' contraction $\gz \nabla \gz N_i : \boldsymbol{\mathcal{G}} \gz g$\;
          evaluate $\gz g_s := \gz \nabla_{sym} \gz x$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{C}}\gz g_s = \boldsymbol{\mathcal{C}}\gz : \gz g_s$ \tcp*{2nd order symmetric}
          ``submit'' contraction $\gz \nabla_{sym} \gz N_i : \boldsymbol{\mathcal{C}}\gz g_s$ \;
        }
  }
  \caption{Matrix-free tangent cell operator: cache fourth order material tangent $\boldsymbol{\mathcal{C}}$ and Kirchhoff stress $\gz \tau$.}
  \label{alg:mf_tensor4}
\end{algorithm}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{Emmy_RRZE_timing2d.eps}
      \caption{vmult 2D}
      \label{fig:benchmark_miehe_Emmy_vmult2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_timing3d.eps}
    \caption{vmult 3D}
    \label{fig:benchmark_miehe_Emmy_vmult3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{Emmy_RRZE_memory2d.eps}
      \caption{memory consumption 2D}
      \label{fig:benchmark_miehe_Emmy_memory2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_memory3d.eps}
    \caption{memory consumption 3D}
    \label{fig:benchmark_miehe_Emmy_memory3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_cg2d.eps}
    \caption{CG iterations 2D}
    \label{fig:benchmark_miehe_Emmy_cg2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_cg3d.eps}
    \caption{CG iterations 3D}
    \label{fig:benchmark_miehe_Emmy_cg3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_solver2d.eps}
    \caption{CG solution time 2D}
    \label{fig:benchmark_miehe_Emmy_sol2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_solver3d.eps}
    \caption{CG solution time 3D}
    \label{fig:benchmark_miehe_Emmy_sol3}
  \end{subfigure}
  \caption{Emmy cluster, RRZE.}%
  \label{fig:benchmark_miehe_Emmy}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{IWR_timing2d.eps}
      \caption{vmult 2D}
      \label{fig:benchmark_miehe_IWR_vmult2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_timing3d.eps}
    \caption{vmult 3D}
    \label{fig:benchmark_miehe_IWR_vmult3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{IWR_memory2d.eps}
      \caption{memory consumption 2D}
      \label{fig:benchmark_miehe_IWR_memory2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_memory3d.eps}
    \caption{memory consumption 3D}
    \label{fig:benchmark_miehe_IWR_memory3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_cg2d.eps}
    \caption{CG iterations 2D}
    \label{fig:benchmark_miehe_IWR_cg2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_cg3d.eps}
    \caption{CG iterations 3D}
    \label{fig:benchmark_miehe_IWR_cg3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_solver2d.eps}
    \caption{CG solution time 2D}
    \label{fig:benchmark_miehe_IWR_sol2}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_solver3d.eps}
    \caption{CG solution time 3D}
    \label{fig:benchmark_miehe_IWR_sol3}
  \end{subfigure}
  \caption{IWR cluster.}%
  \label{fig:benchmark_miehe_IWR}
\end{figure}

>>>>

\section{Matrix-free operator evaluation}
\label{sec:mf}
Classically in order to solve \eqref{eq:linear_system}, the matrix $\gz A$ and the force vector $\gz F$ corresponding to the discretization are assembled and
a direct or iterative solver is used to solve the linear system.
On modern computer architectures however, it turns out that loading data is significantly slower than performing the arithmetic operations when solving.
For this reason, recent implementations often focus on so-called matrix-free approaches. The idea is to perform the operations in the solver on-the-fly
rather than loading matrix elements from memory.
For iterative solvers, this is possible since it is sufficient to compute matrix-vector products.
%
The matrix-vector product $A x$ can be expressed by
\begin{align*}
 (Ax)_i &= \sum_j a(\gz N_i,\gz N_j) x_j \\
        &= \sum_K\sum_q \sum_j \tilde{a}(\gz N_i,\gz N_j)(\gz x_q) x_j w_q
\end{align*}
where in the last step $\tilde{a}_K(\varphi_i,\varphi_j)(\gz x_q)$ is a representation for the evaluation of the bilinear in one quadrature point and a quadrature rule is used.
For the sake of demonstration, let us assume $A$ represents a mass matrix. In this case, it holds
\begin{align*}
 \tilde{a}_K(N_i,N_j)(\gz x_q) = N_i(\gz x_q)N_j(\gz x_q).
\end{align*}
Further assuming that the number of the one-dimensional quadrature points $n$ matches the degree of the ansatz space plus one, the evaluation of all the shape functions ($n^d$)
in all quadrature points ($n^d$) has complexity $\mathcal{O}(n^{2d})$ in case we consider a problem in $d$ space dimensions. For the total matrix-vector product we get $\mathcal{O}(2n^{2d})$
and this is the same as for a regular matrix-vector where the entries are already precomputed. Assuming tensor product ansatz spaces and a tensor product quadrature rule, we can actually do better
than that. Indeed, the evaluation of all the shape functions in all the ansatz points can be rewritten as
\begin{lstlisting}
template<int k, int q>
void evaluate_dof_vector_in_all_quadrature_points
  (const double u[k][k][k],
   const double phi[k][q],
   double return_value[q][q][q])
{
  double tmp1[k][k][q] {};
  for (int i1=0; i1<k; ++i1)
    for (int i2=0; i2<k; ++i2)
      for (int q3=0; q3<q; ++q3)
        for (int i3=0; i3<k; ++i3)
          tmp1[i1][i2][q3] += u[i1][i2][i3]*phi[i3][q3];

@@

\begin{algorithm}[!ht]
  \SetKwInOut{Input}{Given}
  \SetKwInOut{Output}{Return}
  \Input{RHS FE vector $\gz x$, current FE solution $\overline{\gz u^h}$,
  cacheed $c_1 := \mu - 2 \lambda \log(J)$ for each cell and quadrature point}
  \Output{action of the FE tangent \eqref{eq:algebraic_tangent} on $\gz x$}
  \ForEach{ element $K \in \Omega^h$ }{
        \ForEach{quadrature point $q$ on $K$}{
          evaluate $\gz \nabla_X \gz u^h$ \tcp*{2nd order}
          evaluate $\gz F = \gz I + \gz \nabla_X \gz u^h$ \tcp*{2nd order}
          evaluate $J = \rm{det}(\gz F)$ \tcp*{scalar}
          evaluate $\gz b = \gz F \cdot \gz F^T$ \tcp*{2nd order symmetric}
          evaluate $\gz g := \gz \nabla \gz x$ \tcp*{2nd order}
          evaluate $\gz \tau = \mu \gz b - c_1 \gz I$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{G}} \gz g = \gz g \cdot \gz \tau/J$ \tcp*{2nd order}
          ``submit'' contraction $\gz \nabla \gz N_i : \boldsymbol{\mathcal{G}} \gz g$\;
          evaluate $\gz g_s := \gz \nabla_{sym} \gz x$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{C}}\gz g_s = \left[2 c_1 \gz g_s + 2 \lambda\, \rm{tr}( \gz g_s) \gz I \right]/J$ \tcp*{2nd order symmetric}
          ``submit'' contraction $\gz \nabla_{sym} \gz N_i : \boldsymbol{\mathcal{C}}\gz g_s$ \;
        }
  }
  \caption{Matrix-free tangent cell operator: scalar cache}
  \label{alg:mf_scalar}
\end{algorithm}

@@

\begin{algorithm}[!ht]
  \SetKwInOut{Input}{Given}
  \SetKwInOut{Output}{Return}
  \Input{RHS FE vector $\gz x$,
  cached
  $c_1 := 2\left[\mu - 2 \lambda \log(J)\right]/J$,
  $c_2 := 2\lambda/J$ and $\gz \tau/J$ for each cell and quadrature point,
  evaluated based on $\overline{\gz u^h}$}
  \Output{action of the FE tangent \eqref{eq:algebraic_tangent} on $\gz x$}
  \ForEach{ element $K \in \Omega^h$ }{
        \ForEach{quadrature point $q$ on $K$}{
          evaluate $\gz g := \gz \nabla \gz x$ \tcp*{2nd order}
          evaluate $\boldsymbol{\mathcal{G}}\gz g = \gz g \cdot \left[\gz \tau/J \right]$ \tcp*{2nd order}
          ``submit'' contraction $\gz \nabla \gz N_i : \boldsymbol{\mathcal{G}} \gz g$ \;
          evaluate $\gz g_s := \gz \nabla_{sym} \gz x$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{C}} \gz g_s = c_1 \gz g_s + c_2 \, \rm{tr}(\gz g_s) \gz I$ \tcp*{2nd order symmetric}
          ``submit'' contraction $\gz \nabla_{sym} \gz N_i : \boldsymbol{\mathcal{C}} \gz g_s $ \;
        }
  }
  \caption{Matrix-free tangent cell operator, variant 1: cache second order Kirchhoff stress $\gz \tau$ and thereby avoid the need to evaluate refential quantities like $\gz F$ at runtime.}
  \label{alg:mf_tensor2}
\end{algorithm}

@@

\begin{algorithm}[!ht]
  \SetKwInOut{Input}{Given}
  \SetKwInOut{Output}{Return}
  \Input{RHS FE vector $\gz x$,
  cached $\gz \tau/J$ and $\boldsymbol{\mathcal{C}}$ for each cell and quadrature point,
  evaluated based on $\overline{\gz u^h}$}
  \Output{action of the FE tangent \eqref{eq:algebraic_tangent} on $\gz x$}
  \ForEach{ element $K \in \Omega^h$ }{
        \ForEach{quadrature point $q$ on $K$}{
          evaluate $\gz g := \gz \nabla \gz x$ \tcp*{2nd order}
          evaluate $\boldsymbol{\mathcal{G}} \gz g = \gz g \cdot \left[\gz \tau/J\right]$ \tcp*{2nd order}
          ``submit'' contraction $\gz \nabla \gz N_i : \boldsymbol{\mathcal{G}} \gz g$\;
          evaluate $\gz g_s := \gz \nabla_{sym} \gz x$ \tcp*{2nd order symmetric}
          evaluate $\boldsymbol{\mathcal{C}}\gz g_s = \boldsymbol{\mathcal{C}}\gz : \gz g_s$ \tcp*{2nd order symmetric}
          ``submit'' contraction $\gz \nabla_{sym} \gz N_i : \boldsymbol{\mathcal{C}}\gz g_s$ \;
        }
  }
  \caption{Matrix-free tangent cell operator: cache fourth order material tangent $\boldsymbol{\mathcal{C}}$ and Kirchhoff stress $\gz \tau$.}
  \label{alg:mf_tensor4}
\end{algorithm}

@@

\subsection{Matrix-vector multiplication}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{Emmy_RRZE_timing2d.eps}
      \caption{vmult 2D}
      \label{fig:benchmark_miehe_Emmy_vmult2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_timing3d.eps}
    \caption{vmult 3D}
    \label{fig:benchmark_miehe_Emmy_vmult3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{Emmy_RRZE_memory2d.eps}
      \caption{memory consumption 2D}
      \label{fig:benchmark_miehe_Emmy_memory2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_memory3d.eps}
    \caption{memory consumption 3D}
    \label{fig:benchmark_miehe_Emmy_memory3}
  \end{subfigure}
  \caption{Emmy cluster, RRZE, matrix-vector multiplication.}%
  \label{fig:benchmark_miehe_Emmy}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{IWR_timing2d.eps}
      \caption{vmult 2D}
      \label{fig:benchmark_miehe_IWR_vmult2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_timing3d.eps}
    \caption{vmult 3D}
    \label{fig:benchmark_miehe_IWR_vmult3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{IWR_memory2d.eps}
      \caption{memory consumption 2D}
      \label{fig:benchmark_miehe_IWR_memory2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_memory3d.eps}
    \caption{memory consumption 3D}
    \label{fig:benchmark_miehe_IWR_memory3}
  \end{subfigure}
  \caption{IWR cluster, matrix-vector multiplication}%
  \label{fig:benchmark_miehe_IWR}
\end{figure}

\subsection{Iterative solver}

\begin{figure}[!ht]
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_cg2d.eps}
    \caption{CG iterations 2D}
    \label{fig:benchmark_miehe_Emmy_cg2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_cg3d.eps}
    \caption{CG iterations 3D}
    \label{fig:benchmark_miehe_Emmy_cg3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_solver2d.eps}
    \caption{CG solution time 2D}
    \label{fig:benchmark_miehe_Emmy_sol2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Emmy_RRZE_solver3d.eps}
    \caption{CG solution time 3D}
    \label{fig:benchmark_miehe_Emmy_sol3}
  \end{subfigure}
  \caption{Emmy cluster, RRZE, iterative solver.}%
  \label{fig:benchmark_miehe_Emmy_cg}
\end{figure}

\begin{figure}[!ht]
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_cg2d.eps}
    \caption{CG iterations 2D}
    \label{fig:benchmark_miehe_IWR_cg2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_cg3d.eps}
    \caption{CG iterations 3D}
    \label{fig:benchmark_miehe_IWR_cg3}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_solver2d.eps}
    \caption{CG solution time 2D}
    \label{fig:benchmark_miehe_IWR_sol2}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{IWR_solver3d.eps}
    \caption{CG solution time 3D}
    \label{fig:benchmark_miehe_IWR_sol3}
  \end{subfigure}
  \caption{IWR cluster.}%
  \label{fig:benchmark_miehe_IWR_cg}
\end{figure}
